\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/appendix.tex
fix: change the reasoning example

            What is the oxidation number of the metal in the compound  \ce{[ZrF_{7}]3-} \\

@@

In addition, as shown in \Cref{tab:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

@@

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples for each of the required skills considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different \enquote{requires} skills, i.e. Reasoning and Calculation.}
    \label{tab:chembench_corpus_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
            \midrule
            Which of the following salts is an acidic salt? \\
            A. \ce{NH4Cl} \\
            B. \ce{Na2CO3} \\
            C. \ce{NaH2PO4} \\
            D. \ce{Zn(OH)Cl} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
            \midrule
            How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
            A. By atomic force microscopy \\
            B. By transform infrared spectroscopy \\
            C. By measuring a photoluminescence spectrum \\
            D. By absorption spectroscopy \\
            \midrule
            \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START\_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C\@\@H]1O[END\_SMILES] \\
            B. [START\_SMILES]Cc1ccccc1N=C(S)N1CCC(NC\-(=O)c2ccco2)CC1[END\_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
            \midrule
            Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \SI{595}{g mol^{-1}} using end-group analysis, where \SI{0.1619}{g} of PLA was dissolved in \SI{25}{cm^3} of benzyl alcohol and titrated with \SI{0.0400}{mol dm^{-3}} \ce{KOH} solution. The volume of \ce{KOH} solution required to reach the endpoint was \SI{6.81}{cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

@@

In analyzing the performance of state-of-the-art models on the ChemBench corpus, we identified several chemical topics where the models consistently struggled to provide correct answers. The following table \cref{tab:chembench_corpus_models_failed_topic} presents examples of challenging questions across different chemical domains, highlighting specific areas where current models need improvement

>>>>

            What is the oxidation number of the metal in the compound \ce{[ZrF_{7}]3-}? \\

@@

In addition, as shown in \Cref{fig:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

@@

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples for each of the required skills considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different \enquote{requires} skills, i.e. Reasoning and Calculation.}
    \label{tab:chembench_corpus_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
            \midrule
            Which of the following salts is an acidic salt? \\
            A. \ce{NH4Cl} \\
            B. \ce{Na2CO3} \\
            C. \ce{NaH2PO4} \\
            D. \ce{Zn(OH)Cl} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
            \midrule
            In an electrochemical system, the standard potential for the hydrogen evolution reaction \\ce{2H+ + 2e- -> H2} is \\pu{-0.07 V}, and for \\ce{Br-} oxidation is \\pu{1.02 V} vs. \\ce{Ag/AgBr}. During an experiment, it's observed that the onset potential for hydrogen evolution has shifted towards a higher potential, while the onset potential for \\ce{Br-} oxidation has shifted towards a lower potential, compared to their respective standard potentials. Which of the following explanations is most likely correct?
            A. The electrode material has changed, causing catalytic effects that alter the onset potentials. \\
            B. There is probably a change in temperature, which affects reaction kinetics. \\
            C. This is due to changes in concentration of reactants and products, following the Nernst equation. \\
            D. This observation is due to experimental error. \\
            \midrule
            \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START\_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C\@\@H]1O[END\_SMILES] \\
            B. [START\_SMILES]Cc1ccccc1N=C(S)N1CCC(NC\-(=O)c2ccco2)CC1[END\_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
            \midrule
            Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \SI{595}{g mol^{-1}} using end-group analysis, where \SI{0.1619}{g} of PLA was dissolved in \SI{25}{cm^3} of benzyl alcohol and titrated with \SI{0.0400}{mol dm^{-3}} \ce{KOH} solution. The volume of \ce{KOH} solution required to reach the endpoint was \SI{6.81}{cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

@@

In analyzing the performance of state-of-the-art models on the \chembench corpus, we identified several chemical topics where the models consistently struggled to provide correct answers. The following table \cref{tab:chembench_corpus_models_failed_topic} presents examples of challenging questions across different chemical domains, highlighting specific areas where current models need improvement
